---
title: "R Notebook"
output: html_notebook
---

1. In this module we will practice using Matrix and Data frame structures in R, using two
lesson from the swirl package. Again, open R-Studio and write the following code in
the console panel.
(a) Create vectors for each group and check the means.
(b) Create a dataframe for these three vectors.
(c) Visualize the the groups using boxplot.
(d) We are assuming that the distribution of samples are approximately normally distributed. To investigate weather there is any significant difference among the means
of these three groups, apply aov command which runs ANOVA test.

```{r}
group1 = c(18.2,20.1,17.6,16.8, 18.8, 19.7, 19.1)
group2 = c(17.4,18.7, 19.1, 16.4, 15.9, 18.4, 17.7)
group3 = c(15.2,18.8,17.7,16.5,15.9,17.1,16.7)
mean(group1)
mean(group2)
mean(group3)
observations = c(group1, group2 , group3)
group_numbers = rep(1:3, rep(7,3))
group_numbers
data_groups = data.frame(observation=observations,group_number=group_numbers)
data_groups
```

```{r}
boxplot(observations~group_numbers, data=data_groups)
```
```{r}
summary(aov(observation~group_number, data=data_groups))
```
```{r}

```
#Load the ISwR library and look at the red.cell.folate data. This dataset contains
#data on red cell folate levels in patients receiving three different methods of ventilation
#during anesthesia. Read the description provided in R. This will give you more domain
#knowledge about the data.
#(a) Visualize the distribution of each ventilation method using boxplot.
#(b) Find out whether at least one method of ventilation during anesthesia have outstanding effect on the red folates.
```{r}
install.packages('ISwR')
library(ISwR)
red.cell.folate <- ISwR::red.cell.folate
boxplot(folate~ventilation, data=red.cell.folate)
summary(aov(folate~ventilation), data= red.cell.folate)
```
```{r}
modified_juul<- ISwR::juul
modified_juul$tanner<- factor(modified_juul$tanner,labels=c("I","II","III","IV","V"))
summary(aov(igf1~tanner,data=modified_juul))
```

